Cochain level May-Steenrod operations

### 2021-07-30 steenrod.tex
Fix broken ref to medina2021adem and update bib of my papers

For the even prime, constructive proofs at the cochain level of the Adem and Cartan relations have been given respectively in \cite{brumfiel2020cochain} and \cite{medina2020cartan}.

>>>>

For the even prime, constructive proofs at the cochain level of the Adem and Cartan relations have been given respectively in \cite{medina2020adem} and \cite{medina2020cartan}.
